\documentclass[a4ppaper, 10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{multicol}

\geometry{margin=1in}

\newcommand{\heading}[1]{\vspace{6pt}\noindent\textbf{\large #1}\vspace{4pt}\\}
\newcommand{\subheading}[1]{\vspace{2pt}\noindent\textbf{#1}\par}

\hypersetup{
	pdftitle={Ethan Glover Resume},
	pdfauthor={Ethan Glover}
}

\begin{document}
	% Name and contact information
	\begin{center}
		{\LARGE \textbf{Ethan Glover}} \\
		Chesterfield, MO, 63017
		\begin{multicols}{2}
			\raggedright
			Email: \href{mailto:hello@ethang.email}{hello@ethang.email} \\
			Phone: +1-816-542-0568 \\
			LinkedIn: \href{https://www.linkedin.com/in/ethan-glover/}{linkedin.com/in/ethan-glover/} \\
			GitHub: \href{https://github.com/eglove}{github.com/eglove}
		\end{multicols}
	\end{center}
	
	\hrule
	
	% Experience Section
	\heading{Experience}
	\subheading{Independent Consultant}
	\raggedright
	\textit{Remote \hfill April 2024 -- Current} \\
	\begin{itemize}[itemsep=0pt, topsep=2pt]
		\item Worked on multiple projects such as creating a React Native app for a local small business building an ERP.
		\item Consulted on building a highly performant dashboard with real-time crypto pricing.
		\item Developed and maintained a CMS-driven React site for a village trustee board.
		\item \textbf{Tech Used:} ESLint, HTML/CSS, JavaScript, React, React Native, SolidJS, Solid Start, Sanity, Tailwind, TypeScript, C\#/.NET, Docker, GitHub, NextUI, NodeJS, Playwright, StoryBook, Vitest, Monorepo, NextJS
		\item \textbf{Methodologies Used:} Dependency Injection, Accessibility, Composable Design, Crab Testing, REST, TDD
	\end{itemize}
	
	\subheading{Software Consultant}
	\raggedright
	\textit{LegrandAV, Remote \hfill November 2023 -- May 2024}
	\begin{itemize}[itemsep=0pt, topsep=2pt]
		\item Led an upgrade from vanilla React and Sitecore to Next.js. The project had been at a standstill for 2 months due to hosting problems. We got it running within a few weeks and moved on to a redesign of the user dashboard. I encouraged the team to move away from outsourcing to markup services for frontend work and make use of accessible libraries such as NextUI.
		\item \textbf{Tech Used:} Azure App Service, C\#/.NET, GraphQL, HTML/CSS, JavaScript, NextJS, React, Redux, Sitecore, Tailwind, TypeScript
		\item \textbf{Methodologies Used:} Dependency Injection, Accessibility, Composable Design, Crab Testing, REST, TDD
		\item \textbf{Reason for leaving:} Contract with no possibility of extension.
	\end{itemize}
	
	\subheading{Software Contractor}
	\raggedright
	\textit{St. Louis County, St. Louis, MO \hfill June 2023 -- August 2023}
	\begin{itemize}[itemsep=0pt, topsep=2pt]
		\item Introduced automated testing to legacy codebases by setting up and writing unit tests for .NET backends as well as E2E and accessibility testing for React frontends. The challenge with introducing tests to legacy codebases is that test runners sometimes expect the best practices that they enforce. For example, React state was not being handled immutably. While it seemed the applications were fine on manual review, tests revealed different states between renders. This was causing many difficult to reproduce bugs. This means getting tests set up would require significant refactoring, even entire rewrites. This is why we pivoted to a focus on E2E as much as possible.
		\item \textbf{Tech Used:} C\#/.NET, Bootstrap, Entity Framework, HTML/CSS, JavaScript, Moq, Playwright, React, TypeScript, XUnit
		\item \textbf{Methodologies Used:} Accessibility, Composable Design, Crab Testing, Dependency Injection, MVC, On-Prem Hosting, REST, TDD
		\item \textbf{Reason for Leaving:} Contract with no possibility of extension.
	\end{itemize}
	
	\pagebreak
	
	\subheading{Software Contractor}
	\raggedright
	\textit{Proagrica, St. Louis, MO \hfill December 2022 -- May 2023}
	\begin{itemize}[itemsep=0pt, topsep=2pt]
		\item Worked with a highly dynamic farming dashboard for an international audience. Made use of Redux to manage complex state interactions and used time travel debugging to discover existing state, debug, and build new features
		\item \textbf{Tech Used:} C\#/.NET, Docker, Entity Framework, ESLint, GitLab, HTML/CSS, i18next, JavaScript, Jira, MediatR, NodeJS, React, React Testing Library, ReactPDF, Redux, StoryBook, Tailwind, TypeScript, Zod
		\item \textbf{Methodologies Used:} Accessibility, Agile, Dependency Injection, REST, TDD
		\item \textbf{Reason for Leaving:} Contract with no possibility of extension, company was reducing dependence on contract teams and only accepting applications for people near offices.
	\end{itemize}
	
	\subheading{Software Consultant}
	\raggedright
	\textit{EPA, Remote \hfill June 2022 -- November 2022}
	\begin{itemize}[itemsep=0pt, topsep=2pt]
		\item Helped rebuild Emissions Collection and Monitoring System (ECMPS) for reporting emission data with a new tech stack. I was one of three developers building the backend. We made an effort to always increase test coverage. The result was QA asking for us to slow down because our production was too fast and not revealing issues. This gave us time to produce more reproducible examples and help QA to ensure the highest quality possible.
		\item \textbf{Tech Used:}  AWS, GitHub, HTML/CSS, JavaScript, Jest, NestJS, NodeJS, React, Redux, SQL, TypeORM, TypeScript, USWDS
		\item \textbf{Methodologies Used:} Agile, Dependency Injection, REST, TDD
		\item \textbf{Reason for Leaving:} Contract with no possibility of extension, after searching it seems the EPA does not often hire full time.
	\end{itemize}
	
	\subheading{Software Contractor}
	\raggedright
	\textit{8Base, Remote \hfill March 2022 -- May 2022}
	\begin{itemize}[itemsep=0pt, topsep=2pt]
		\item Worked on a low-code platform for a startup generating GraphQL APIs through a React-based user interface.
		\item \textbf{Tech Used:}  AWS, AWS Lambda, GraphQL, HTML/CSS, JavaScript, NodeJS, React, SQL, TypeGraphQL, TypeScript
		\item \textbf{Methodologies Used:} Agile
		\item \textbf{Reason fo Leaving:} US team laid off shortly after being hired.
	\end{itemize}
	
	\subheading{Software Engineer}
	\raggedright
	\textit{Avatara, St. Louis, MO \hfill July 2021 -- March 2022}
	\begin{itemize}[itemsep=0pt, topsep=2pt]
		\item Built a team collaboration app from scratch which included features such as P2P video conferences, chat, phone calls, calendar, file sharing and more. All with realtime notifications between users and teams provided by websockets and styled with CSS modules. I was by myself on this project tasked with bringing a general idea to life.
		\item \textbf{Tech Used:}  Monorepo, Apollo, C\#/.NET, GraphQL, HTML/CSS, JavaScript, NextJS, NodeJS, NX, Prisma, React, Rust, SQL, Stencil, Twilio, TypeScript, WebAssembly, WebRTC, WebSockets
		\item \textbf{Methodologies Used:} Monorepo, On-Prem Hosting
		\item \textbf{Reason for Leaving:} Could not get feedback on work, communication was difficult, I was working entirely by myself.
	\end{itemize}
	
	\pagebreak
	
	\subheading{Software Contractor}
	\raggedright
	\textit{Prologue, St. Louis, MO \hfill January 2021 -- July 2021}
	\begin{itemize}[itemsep=0pt, topsep=2pt]
		\item Worked with an application for delivering quotes and booking shipments for clients through multiple logistics carriers such as FedEx, UPS, and others.
		\item \textbf{Tech Used:}  HTML/CSS, JavaScript, Laravel, PHP, Vue, Yii
		\item \textbf{Methodologies Used:} REST
		\item \textbf{Reason for Leaving:} Contract to hire, did not see opportunity for career growth.
	\end{itemize}
	
	\subheading{Software Contractor}
	\raggedright
	\textit{CenturyLink, St. Louis, MO \hfill May 2020 -- December 2020}
	\begin{itemize}[itemsep=0pt, topsep=2pt]
		\item Redesigned customer dashboard with CenturyLink for users managing their accounts with vanilla JavaScript and CSS stylesheets. Maintained compatibility with Internet Explorer 11.
		\item \textbf{Tech Used:}  Apache Velocity, HTML/CSS, Java, JavaScript, Jira, Spring Boot, Subversion (SVN), TypeScript, Vue
		\item \textbf{Methodologies Used:} Agile
		\item \textbf{Reason for Leaving:} Contract to hire, team was downsizing at the end fo the contract, I was invited to apply for the parent company Lumen but did not have the right experience.
	\end{itemize}
	
	\subheading{Software Freelancer}
	\raggedright
	\textit{Freelance, Remote \hfill November 2018 -- May 2020}
	\begin{itemize}[itemsep=0pt, topsep=2pt]
		\item Consulted with OneSpiritOneWorld.org, a non-profit working to end dog homelessness and abuse to improve SEO and page performance as well. Encouraged a heavier social media presence.
		\item Worked with 2 National Radio station on SEO and web consulting.
		\item \textbf{Tech Used:}  GraphQL, HTML/CSS, JavaScript, NodeJS, React
		\item \textbf{Methodologies Used:} SEO
		\item \textbf{Reason for Leaving:} Looking to start career.
	\end{itemize}
\end{document}