\documentclass[a4ppaper, 10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{multicol}

\geometry{margin=1in}

\newcommand{\heading}[1]{\vspace{6pt}\noindent\textbf{\large #1}\vspace{4pt}\\}
\newcommand{\subheading}[1]{\vspace{2pt}\noindent\textbf{#1}\par}

\hypersetup{
	pdftitle={Ethan Glover Resume},
	pdfauthor={Ethan Glover}
}

\begin{document}
	% Name and contact information
	\begin{center}
		{\LARGE \textbf{Ethan Glover}} \\
		Chesterfield, MO, 63017
		\begin{multicols}{2}
			\raggedright
			Email: \href{mailto:hello@ethang.email}{hello@ethang.email} \\
			Phone: +1-816-542-0568 \\
			LinkedIn: \href{https://www.linkedin.com/in/ethan-glover/}{linkedin.com/in/ethan-glover/} \\
			GitHub: \href{https://github.com/eglove}{github.com/eglove}
		\end{multicols}
	\end{center}
	
	\hrule
	
	% Experience Section
	\heading{Experience}
	\subheading{Software Contractor}
	\raggedright
	\textit{Remote \hfill November 2018 -- Current} \\
	\begin{itemize}[itemsep=0pt, topsep=2pt]
		\item Multiple contracts working with many different stacks. Primarily React as a frontend, and many backend technologies such as Node, .NET, Java and PHP.
		\item With St. Louis County, introduced automated testing to legacy codebases by setting up and writing unit tests for .NET backends as well as E2E and accessibility testing for React frontends.
		\item At Proagrica, I worked with a highly dynamic farming dashboard for an international audience.
		\item With the EPA, I helped rebuild Emissions Collection and Monitoring System (ECMPS) for reporting emission data with NodeJS and NestJS.
	\end{itemize}
	
	\subheading{OTR Driver}
	\raggedright
	\textit{Roehl Transport \hfill Dec 2018 -- Aug 2019}
	\begin{itemize}[itemsep=0pt, topsep=2pt]
		\item Check vehicle to ensure that mechanical, safety and emergency equipment is in good working order. 
		\item Maneuver truck into loading or unloading positions, following signals from loading crew and checking that vehicle and loading equipment are properly positioned.
		\item Maintain logs of working hours or of vehicle service or repair status, following applicable state and federal regulations.
		\item Report vehicle defects, accidents, traffic violations, or damage to the vehicle.
	\end{itemize}
	
	\subheading{Delivery Driver}
	\raggedright
	\textit{Peoples Linen Rental, Keene, NH \hfill Nov 2016 -- Nov 2018}
	\begin{itemize}[itemsep=0pt, topsep=2pt]
		\item Load and unload truck.
		\item Verify the contents of inventory loads against shipping papers.
		\item Report delays, accidents, or other traffic and transpiration situations to bases or other vehicles.
		\item Obey traffic laws and follow established traffic and transportation procedures.
	\end{itemize}
	
	\subheading{Delivery Driver}
	\raggedright
	\textit{Crossroads Pizza \& Subs, Fitzwilliam, NH \hfill May 2015 -- Nov 2016}
	\begin{itemize}[itemsep=0pt, topsep=2pt]
		\item Inspected and delivered outgoing food deliveries.
		\item Independently solved customer issues on site with food or delivery times.
		\item Performed tasks such as washing dishes, cleaning floors and counters, organizing and maintaining food stock.
		\item Inventoried stock and received incoming food orders.
	\end{itemize}
	
	\subheading{Signal Systems Support Specialist}
	\raggedright
	\textit{U.S. Army}
	\begin{itemize}[itemsep=0pt, topsep=2pt]
		\item Responsible for installation, operation and maintenance of radio and data distribution systems; ensured all orders were completed on time and met U.S. Army standards.
		\item Technical assistance and training for local area networks and routers, signal communications and offering support for satellite radio and communications equipment functions. Installed, maintained and conducted troubleshooting measures on terminal devices.
		\item Operated and performed proactive preventive maintenance checks and services on assigned vehicles and power generators.
	\end{itemize}
\end{document}